Model

### 2019-10-13 stats/model.Rmd
update model
add 200k 8chain model comparison

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 25000,
                        burn = 20000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_25k_model_comparison_noise.rds")

sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_model_comparison.rds")

>>>>

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 8,
  cores = 8,
  inference_opts = list(method = "incrementalMH",
                        samples =200000,
                        burn = 100000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 5000)
)

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison_noise.rds")

#sem_know_model <- readRDS("../saves/sem_know_model_variant3_100k_model_comparison.rds")
